From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-09 papers/ACL2020/introduction.tex
increase coherence of sections 1-2-3; shortening still required

\cs{need to make clear the diff btw objects meaning the concept/class and meaning an instance}
\cs{need to discuss problematic of standard evaluation procedure of CV models}

>>>>

Objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal} etc.). 
The task of \emph{object naming} -- generating not just a formally correct but also an appropriate, \emph{natural} name for an object -- is distinct from the closely related tasks of object detection and image classification (see below).
It has been studied in psycholinguistics~\cite{refs} \mw{Refs!}, but has received comparatively little attention in \langvis (\lv) and computational linguistics (CL) research.
We address the following question:\\
\fbox{\parbox{\columnwidth}{\textbf{Q:} Can standard object detection/image classification models (be fine-tuned to) exhibit human-like object naming behavior?}}\\\\
In particular, we test several models for their ability to generate \emph{entry-level names}, i.e., the names people prefer when calling a specific object (e.g.,~\name{duck} in Figure~\ref{fig:duck}, right image).
We wish to find out, for instance, whether different types of models or training regimes will tend towards different kinds of human-like errors in this regard.
A secondary contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (\mn, Anonymous, under review) with extensive quality control, the resulting data of which we also describe and make available with this paper.

In \lv, the choice of a particular name for an object is a ubiquitous problem -- it underlies virtually all tasks that model how speakers use language to refer to objects in the world, such as image description, visual question answering and referring expression generation.
\lv methods are generally based on object detection or image classification models from computer vision (CV) research (or the visual features extracted from them) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (e.g., \name{bus}) while others seem overly specific (e.g.,\ \name{goblet, gyromitra}; cf.\ the label inventory of the ILSVRC challenges; \citealt{ILSVRC15}).
Pre-training on such labels has its justification in that computer vision models can learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs. slightly pointed). 
But it raises the issue of whether these models could be used for more human-like object naming.
% Accordingly, these CV models are assessed by their ability to predict a single, in cases very specific, ground-truth label.

% By contrast, the goal of \lv object naming models is to predict the `natural' name of an object, i.e.,~the name a human could choose for the object instance.
Psycholinguistic studies have found that humans have a preference towards a particular name, defined as the \textit{entry-level name}, when naturally naming an object \cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}. 
However, this research has traditionally focused on \categories and/or their prototypical/schematic depictions (e.g., \newcite{rossion2004revisiting}), as opposed to the situated instances in naturalistic images with which \lv is mostly concerned.
Humans may prefer different names for different instances of the same \category, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
For example, in Figure~\ref{fig:duck}, for the two instances of a duck (from \vg, with names from \mn), most people (27 out of 36) called the instance on the left \name{bird}, while \name{duck} was strongly preferred for the right instance. 
\begin{figure}[t]
	\centering
	\small
	\begin{tabular}{p{3cm}p{3cm}}
		\centering
		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
	\end{tabular}
	\caption{Different naming preferences for different instances of the same \category \name{duck} in \mn.\label{fig:duck}}
\end{figure}
Hence, both the single-ground-truth view of CV models and the category-level approach predominant in Psycholinguistics are insufficient for assessing the effectiveness of \lv models for human-like, entry-level object naming.
The \mn dataset was designed to help mend this gap: it consists of names entered by 36 annotators in parallel, for 25K objects in naturalistic images from \vg~\cite{krishna2016visualgenome}.
However, the name annotations of \mn have not been verified to filter out incorrect names or names for the wrong object, a problem that is in some sense the opposite of that posed by the single-ground-truth approach.

Our main contributions in this paper are (i) to run the \mn data through a rigorous annotation round to quantify both the adequacy of its names and the types of errors they contain, in order to (ii) test and compare object detection and image classification models for their ability at the task of \emph{instance-based, entry-level object naming}. More precisely, \mn enables us to define the entry-level as follows:\\
\fbox{\parbox{\columnwidth}{\textbf{Entry-level name:} the most common name given to an object instance according to \mn}}\\\\
We evaluate the effectiveness of different models on predicting these entry-level names, and our additional verification annotations enable us to understnad the kinds of mistakes each model makes (e.g.,~a `wrong' prediction may be a less preferred name as opposed to a true error).
We show that generic object classification models on their own (ResNet, Faster-RCNN and Bottom-up) already learn to provide entry-level names for objects, but also that it is possible to apply transfer learning on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models. 
\mw{Remark about the kinds of human errors, just as in the abstract, or some other more interesting teaser?}

%% END OF FILE %%

%Our contributions towards the task of instance-based entry-level naming in \lv and CL research are two-fold:  
%First, we provide data on object naming with real images on a large scale. 
%We take on an empirical notion of entry-level names, and define it on the instance-level, i.e., the name that humans prefer to use when calling a particular object in a real-world image.   
%We extend \mn (under submission), a dataset that provides 36 names for each of 25K objects from \vg~\cite{krishna2016visualgenome}, with information on adequacy and reference of all collected names, which affords rich analysis possibilities. 
%
%Second, we introduce the verified \mn dataset as evaluation data, and provide an extensive analysis of the ability of object detection and classification models to account for entry-level object naming in our dataset.

\iffalse
%However, when they speak, humans in general name specific \textit{instances} of objects---actually, instances in particular situations and points of view, which may humans have prefer different names for instances of the same \category, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).

%Accordingly, datasets used for object naming in Psycholinguistics use idealized drawings that correspond more to categories than to instances~\cite{+++++}.
%
%

Despite its relevance in \lv and CL, the challenge of instance-based natural naming has been overseen. 
\lv research that particularly focuses on the prediction of entry-level names is scarce, and existing work has adopted the \category-based concept of entry-level names \cite{Ordonez:2016}. 
Furthermore, existing datasets lack necessary information to make progress in \lv and CL research on this phenomenon. 
\cs{TODO@CS: EVALUATION ISSUE GOES HERE.}
\begin{itemize}
	\item resources developed in CV and \lv can be useful to study object naming. 
	\item However, they provide only one (or a few) name per object \ra no guarantee that it is the entry-level name. (We provide more, to have a robust estimate of entry-level names (as well as data on other possible names). \gbt{actually, maybe move this to the previous part? \ra differences with Psycholing, with CV resources})
	\item object naming has often been conflated with object classification in CV. \gbt{Discuss differences; mention the swan - whatever name it has in wordnet example of ordonez et al?}
	\item a big problem with this approach is that it follows a single-label evaluation. With our data, we show that often model responses are adequate even if they do not correspond to the entry-level name.
	\item we also show that object classification models ``spontaneously'' learn to provide entry-level names for objects
	\item and that it is possible to use \mn to successfully fine-tune existing object detection and classification models to predict entry-level names for objects.
\end{itemize}

This paper seeks to spur \lv and CL research on the problem of \textit{instance-based entry-level object naming}.

Our contributions are two-fold:  
First, we provide data on object naming with real images on a large scale. 
We take on an empirical notion of entry-level names, and define it on the instance-level, i.e., the name that humans prefer to use when calling a particular object in a real-world image.   
We extend \mn (under submission), a dataset that provides 36 names for each of 25K objects from \vg~\cite{+++}, with information on adequacy and reference of all collected names, which affords rich analysis possibilities.

\cs{I'll continue from here.}
Second, we introduce the verified \mn dataset as evaluation data that allows XXX. We provide an extensive analysis of the ability of object detection and classification models on the task of predicting the entry-level names in our dataset.

### 2019-12-09 papers/ACL2020/manynames.tex
increase coherence of sections 1-2-3; shortening still required

\cs{In the remainder of this paper, we will use object and object instance interchangeably.}
\subsection{Overview of ManyNames}
\label{sect:mn_overview}

brief summary of lrec paper, shortcoming, what we added

\begin{itemize}
	\item For each object: a response set comprising all entered names (spellchecked) and their respective counts, i.e., the number of annotators which enter the respective name.
	\item Problems \mw{I already had a go writing a 'bridge' paragraph containing this; see below.}: referential uncertainty: object other than target object was  identified as named
	\item \cs{Mention how agreement on \mn is computed (anticipating that we'll be taking a closer look at this in 3.3 when the verification is in place).}
\end{itemize}

\mw{Sina wrote this in 3.3; I think it should go here in 3.1., in order for 3.3 to more clearly show the added value of verification:}
ManyNames provides a large vocabulary of names (7970) for 25K objects.
Note that this vocabulary is much larger than what state-of-the-art object detectors are typically trained on. 
The vocabulary of entry-level names -- defined for each object as the most frequent name given -- is drastically smaller and contains only 442 types. 
This small set, however, covers at least 50\% of the objects in \vg, i.e. almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.

Manual inspection of the \mn data revealed that annotators occasionally named an object different from the one highlighted by the bounding box (e.g., the name \emph{helmet} when the bounding box highlights an entire motorcyclist), or the right object but with an incorrect name (e.g., ``horse'' for a cow), and sometimes the bounding box may have been unclear.
Although these errors are interesting human data in their own right, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology used for \mn, where there is a financial incentive to complete the task as quickly as possible.
As such they pose a challenge for our research goal, which is to see whether the object-naming ability of computational models resembles those of actual language users.

\subsection{Collecting verification of ManyNames}
\label{sect:mn_verification}

To overcome the aforementioned challenge we collected a new layer of verification annotations on top of \mn.
We recruited annotators from Amazon Mechanical Turk\footnote{
	\url{https://mturk.com}
} (AMT) to categorize the object-name pairs from \mn into various categories (e.g., adequate vs.\ different types of errors), explained below.
Since this is a multiple-choice task (unlike the generation task through which \mn was gathered) we were able to conduct rigorous quality control, ensuring the reliability of our new layer of annotations (see the supplementary material for details).

@@

\mw{I think the following is nice, but strictly redundant, so candidate for deletion if need be:}
Summing up, we provide new verification of \mn, in the form of: name adequacy judgments, type of inadequacy (linguistic, bounding box, named object misinterpreted, other), and information about which names were likely intended for the same object. In relation to our research goal, in section~\ref{sec:analysis} these results will allow us to quantify, for instance, whether the name generated by a given model, if it is not the entry-level name, is at least a name that could reasonably be for the same object as the entry-level name, and whether it is adequate.

@@

\paragraph{Judgment aggregation}
Overall, $255$~participants annotated a total of $69,356$~object-name pairs, with three participants per pair.
We aggregate our name adequacy judgments by taking the mean, and inadequacy type judgments by taking the majority (counting ``none'' for annotators saying there is no inadequacy). 
Average name adequacy, on the scale from totally inadequate (0) to adequate (1), is 0.80 (\mbox{std=$0.093$}).
Inter-annotator agreement is high also by other measures: the proportion of annotators agreeing on ``adequate'' is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
We consider this level of agreement as high given the complexity of the task (e.g., pictures sometimes unclear), especially bearing in mind that we essentially asked our participants to do some kind of mind-reading (i.e., which object could someone who entered an inadequate name plausibly have had in mind?).
Figure~\ref{fig:verification-piechart} shows the proportion of `adequate' judgments and the types of inadequacies our individual annotators reported (a), as well as the aggregated (mean/majority) judgments (b).
\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{images/verification_piechart_double.pdf}\\
	\hspace*{\fill}a.\hspace*{\fill}\hspace*{\fill}b.\hspace*{\fill}\hspace*{\fill}
	\caption{Verification results: a. counting individual annotations; b. counting image-name pairs with their aggregated scores. Lighter shade within a hue indicates slight/possible error of that type; darker shade severe error.}
	\label{fig:verification-piechart}
\end{figure}

As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes: \sameobject and \cluster.
% \cs{This pair-wise view is only because of the need for aggregating the clustering of 3 annotators into one, isn't it? In this case, it would be "aggregating name cluster", no?! So what you did for the first aggregation (modeling) was a pair-wise aggregation?} \mw{I don't understand this...}
First, for analysing computational object naming models (Section~\ref{sec:analysis}), 
% we want to have all valid name alternatives to the entry-level name (or a target name in general), i.e.,~a soft clustering of names. 	% <- Carina's reformulation, but not strictly true and not clear to me.
we want to know primarily whether the name generated by a model, if it isn't the entry-level name, was at least intended for the same object as the entry-level name (i.e., the most frequent name).
This \textbf{\sameobject} measure we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
Second, for a better understanding of the verified \mn data itself (Section~\ref{sect:mn_analysis}) we want to be able, e.g., to assess the mean number of names per object, and for that we need to compute actual \emph{clusters} of names (the pairwise majority rule does not result in a proper clustering). 
%However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
%For this, 
% we need \cs{@MW please check if that's correct} \mw{No it isn't} to compute hard clusters
We compute the \textbf{\cluster} of a name by agglomerative, complete-linkage clustering with a distance threshold of .5, using as distance between two names the proportion of annotators saying they do not name the same object (i.e., this means that all pairs of names in a cluster must name the same object according to a majority of annotators).
\mw{The following is candidate for removal/shortening if we need to save space.}
A possible disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object.
It entails for instance that \emph{food} cannot be clustered both with \emph{pizza} and with the \emph{cheese} on top, even though both are definitely instances of food.
But this is not as problematic as it may seem, because we do not care primarily about such taxonomic relationships--- %(which could be gotten from, e.g., WordNet) -- 
rather, we care about %(and asked our annotators) 
which single object a person who entered \emph{food} was likely intending to name: presumably the pizza as a whole rather than the cheese on top. 
Moreover, although hard clustering may occasionally lead us to \emph{under}estimate the number of names for an object, the alternative, \emph{soft} clustering (where each name could potentially be in multiple clusters) would risk \emph{over}estimating the number of names per object, as well as the number of named objects in an image, both of which would be more harmful to our aims.

@@

\subsection{Analysis}
\label{sect:mn_analysis}

The verification we conducted is necessary for our main research aim -- to evaluate computational object naming models -- but they also enable a deeper understanding of the \mn data.
Table~\ref{tab:stat-entry-level} provides a bird's eye overview.
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{p{5cm}l}
		\toprule		
		objects in MN & 25,315\\
		total vocabulary &  7,970\\
		entry-level vocabulary & 442\\
		objects in VG with name in entry-level vocab & $\sim$ 2M (50\%)\\
		\midrule
		av. agreement all names & 34.9\%\\
		av. agreement entry-level names & 75.2\%\\
		av. agreement entry-level cluster & 42.3\%\\
		\midrule
		av. adequacy all names & 0.81\\
		av. adequacy entry-level names & 0.97 \\
		av. adequacy entry-level cluster & 0.94 \\
		\bottomrule	
	\end{tabular}
	\caption{Basic statistics for entry-level names in \mn. Av.agreement denotes the proportion of annotators (out of 36) that annotated a given name for an object, averaged over all names of a relevant subset.}
	\label{tab:stat-entry-level}
\end{table}
\mw{Add more info to the table, e.g., 1. cluster size.
2. For the instances where VG!=topMN: Percentage of instances where the VG name is among the responses of an \textit{alternative object} (as given by clustering). (for Sect 4)
. 3. Comparison of VG and MN, demonstrating that MN is a more reliable source for entry-level names. (for Sect 4)}

Let us focus on our two main reasons for wanting to use \mn to evaluate computational models, i.e., a dataset where (i) actual contextualized instances are named (not prototypes or classes), and (ii) every instance is named by many annotators.
\cs{Make formulation consistent with what is (was) in the intro:}
Regarding feature (i), recall that the traditional, taxonomic view of object naming regards entry-level names as determinable based on the object's class, meaning that all instances of a class have the same entry-level name. 
Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure~\ref{fig:duck} where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
To quantify this point, let us concentrate on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name -- a very strict requirement which only 281 of the 422 entry-level names of \mn meet.
These names, which are a clear winner at least once, are still on average a clear winner only in 46\% of cases where there is a clear winner at all (SD: .34).
Now, some of this is due to errors of the type we have sought to identify, but the verified results support the same conclusion: 
even restricting attention to cases where the name is adequate and names the right object, they are still a clear winner only in 66\% of cases where there is one (SD: .35, but skewed with about half over 80\%).

@@

%ManyNames was collected in four rounds of 9 annotators each.
%On average, the entry-level name differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
%Figure~\ref{fig:entry-level-name-stability} shows this in a more general way.
%\mw{@gbt: I first did it the way you suggested, i.e., by sampling, but I found the resulting plot (not shown now) too hard to interpret, even a bit misleading. I've kept this text + plot in the TeX source further below, commented out, in case you want to have a look. But I think the following is better:}
Regarding our second reason, feature (ii) mentioned above, Figure~\ref{fig:entry-level-name-stability} shows that gathering many annotations is necessary for reliably identifying entry-level names.
\begin{figure}[t]
	\includegraphics[width=.9\columnwidth]{images/stability_analytic.png}
	\caption{Proportion of objects (vertical) for which the entry-level name can be confidently (95\%) identified after gathering N names (horizontal). \mw{increase plot font size}}
	\label{fig:entry-level-name-stability}
\end{figure}
For each object we estimated, on the basis of its \mn response set, how many names should have been gathered for the entry-level name (as defined on the basis of 36 names) to be the majority name among them with 95\% probability.
The blue line shows that, even after gathering 10 names, the entry-level name is sufficiently likely to be the majority name for only 68\% of objects (i.e.,~for 32\% of objects, there's a greater than 5\% chance of getting a different majority name).
Gathering 20 names increases this to 78\%.
Our verification results let us see that most of the remaining indeterminacy occurs within the entry-level name's \cluster:
the red line is computed by taking only names from the \cluster of the entry-level name into account:
by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily -- but not by much, since names for the wrong object tend not to compete for `most frequent' anyway.
(An analogous plot for the subset of all adequate names essentially coincided with the red line, reflecting that most adequate names were intended for the same object as the entry-level name.)

@@

\cs{If time permits, can you compute Figure~\ref{fig:entry-level-name-stability} individually for each domain, and mention what/if something stands out?} \mw{I did this for the `cat' column, see slack, but you probably meant something different by `domain'. Anyway, there are pretty big differences between domains yes...}

>>>>

\paragraph{Collection procedure}
\label{sect:mn_verification}

We recruited annotators from Amazon Mechanical Turk\footnote{
	\url{https://mturk.com}
} (AMT) to categorize the object-name pairs from \mn into various categories (e.g., adequate vs.\ different types of errors), explained below.
Since this is a multiple-choice task (unlike the generation task through which \mn was gathered) we were able to conduct rigorous quality control, ensuring the reliability of our new layer of annotations (see the supplementary material for details).

@@

%\mw{I think the following is nice, but strictly redundant, so candidate for deletion if need be:}
%Summing up, we provide new verification of \mn, in the form of: name adequacy judgments, type of inadequacy (linguistic, bounding box, named object misinterpreted, other), and information about which names were likely intended for the same object. In relation to our research goal, in section~\ref{sec:analysis} these results will allow us to quantify, for instance, whether the name generated by a given model, if it is not the entry-level name, is at least a name that could reasonably be for the same object as the entry-level name, and whether it is adequate.

@@

\paragraph{Judgment aggregation}
Overall, $255$~participants annotated a total of $69,356$~object-name pairs, with three participants per pair.
We aggregate our name adequacy judgments by taking the mean, and inadequacy type judgments by taking the majority (counting ``none'' for annotators saying there is no inadequacy). 
Average name adequacy, on the scale from totally inadequate (0) to adequate (1), is 0.80 (\mbox{std=$0.093$}).
The proportion of annotators agreeing on adequacy ratings is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
This is high given the complexity of the task, essentially mind-reading what the original \mn annotators may have meant, plus the fact that pictures and bounding boxes are sometimes unclear.
Figure~\ref{fig:verification-piechart} shows the proportion of adequate names and inadequacy types (individual judgments and aggregated).
\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{images/verification_piechart_double.pdf}\\
	\hspace*{\fill}a.\hspace*{\fill}\hspace*{\fill}b.\hspace*{\fill}\hspace*{\fill}
	\caption{Verification results: a. counting individual annotations; b. counting image-name pairs with their aggregated scores. Lighter shade within a hue indicates slight/possible error of that type; darker shade severe error.}
	\label{fig:verification-piechart}
\end{figure}

As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes: \sameobject and \cluster.
% \cs{This pair-wise view is only because of the need for aggregating the clustering of 3 annotators into one, isn't it? In this case, it would be "aggregating name cluster", no?! So what you did for the first aggregation (modeling) was a pair-wise aggregation?} \mw{I don't understand this...}
First, for analysing computational object naming models (Section~\ref{sec:analysis}), 
% we want to have all valid name alternatives to the entry-level name (or a target name in general), i.e.,~a soft clustering of names. 	% <- Carina's reformulation, but not strictly true and not clear to me.
we want to know primarily whether the name generated by a model, if it isn't the entry-level name, was at least intended for the same object as the entry-level name (i.e., the most frequent name).
This \textbf{\sameobject} measure we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
Second, for a better understanding of the verified \mn data itself (Section~\ref{sect:mn_analysis}) we want to be able, e.g., to assess the mean number of names per object, and for that we need to compute actual \emph{clusters} of names (the pairwise majority rule does not result in a proper clustering). 
We compute the \textbf{\cluster} of a name by agglomerative, complete-linkage clustering with a distance threshold of .5, using as distance between two names the proportion of annotators saying they do not name the same object (i.e., this means that all pairs of names in a cluster must name the same object according to a majority of annotators).\footnote{
	The `hard' clustering we use may occasionally lead us to \emph{under}estimate the number of names for an object (this is also why we will use \sameobject and not \cluster in model analysis). The alternative, \emph{soft} clustering (where each name could potentially be in multiple clusters), would risk \emph{over}estimating the number of names per object, as well as the number of named objects in an image.
}

%A possible disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object.
%It entails for instance that \emph{food} cannot be clustered both with \emph{pizza} and with the \emph{cheese} on top, even though both are definitely instances of food.
%But this is not as problematic as it may seem, because we do not care primarily about such taxonomic relationships--- %(which could be gotten from, e.g., WordNet) -- 
%rather, we care about which single object a person who entered \emph{food} was likely intending to name: presumably the pizza as a whole rather than the cheese on top. 
%Moreover, although hard clustering may occasionally lead us to \emph{under}estimate the number of names for an object, the alternative, \emph{soft} clustering (where each name could potentially be in multiple clusters) would risk \emph{over}estimating the number of names per object, as well as the number of named objects in an image.

@@

\paragraph{Analysis}
\label{sect:mn_analysis}

The verification we conducted is necessary for our main research aim -- to evaluate computational object naming models -- but they also enable a deeper understanding of the \mn data.
Table~\ref{tab:stat-entry-level} provides a bird's eye overview.
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{p{5cm}l}
		\toprule		
		objects in MN & 25,315\\
		total vocabulary &  7,970\\
		entry-level vocabulary & 442\\
		objects in VG with name in entry-level vocab & $\sim$ 2M (50\%)\\
		\midrule
		av. agreement all names & 34.9\%\\
		av. agreement entry-level names & 75.2\%\\
		av. agreement entry-level cluster & 42.3\%\\
		\midrule
		av. adequacy all names & 0.81\\
		av. adequacy entry-level names & 0.97 \\
		av. adequacy entry-level cluster & 0.94 \\
		\bottomrule	
	\end{tabular}
	\caption{Basic statistics for entry-level names in \mn. Av.agreement denotes the proportion of annotators (out of 36) that annotated a given name for an object, averaged over all names of a relevant subset.}
	\label{tab:stat-entry-level}
\end{table}
Let us focus on our two main reasons for wanting to use \mn to evaluate computational models, i.e., a dataset where (i) actual contextualized instances are named (not prototypes or classes), and (ii) every instance is named by many annotators.

Regarding feature (i), recall that a traditional view of object naming regards entry-level names as determinable based on the object's class, meaning that all instances of a class have the same entry-level name. 
Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure~\ref{fig:duck} where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
To quantify this point, let us concentrate on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name -- a very strict requirement which only 281 of the 422 entry-level names of \mn meet.
These names, which are a clear winner at least once, are still on average a clear winner only in 46\% of cases where there is a clear winner at all (SD: .34).
Now, some of this is due to errors of the type we have sought to identify, but the verified results support the same conclusion: 
even restricting attention to cases where the name is adequate and names the right object, they are still a clear winner only in 66\% of cases where there is one (SD: .35, but skewed with about half over 80\%).

@@

%ManyNames was collected in four rounds of 9 annotators each.
%On average, the entry-level name differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
%Figure~\ref{fig:entry-level-name-stability} shows this in a more general way.
%\mw{@gbt: I first did it the way you suggested, i.e., by sampling, but I found the resulting plot (not shown now) too hard to interpret, even a bit misleading. I've kept this text + plot in the TeX source further below, commented out, in case you want to have a look. But I think the following is better:}
Regarding our second reason, feature (ii) mentioned above, Figure~\ref{fig:entry-level-name-stability} shows that gathering many annotations is necessary for reliably identifying entry-level names.
\begin{figure}[t]
	\includegraphics[width=.9\columnwidth]{images/stability_analytic.png}
	\caption{Proportion of objects (vertical) for which the entry-level name can be confidently (95\%) identified after gathering N names (horizontal).}
	\label{fig:entry-level-name-stability}
\end{figure}
For each object we estimated, on the basis of its \mn response set, how many names should have been gathered for the entry-level name (as defined on the basis of 36 names) to be the majority name among them with 95\% probability.
The blue line shows that, even after gathering 10 names, the entry-level name is sufficiently likely to be the majority name for only 68\% of objects (i.e.,~for 32\% of objects, there's a greater than 5\% chance of getting a different majority name).
Gathering 20 names increases this to 78\%.
Our verification results let us see that most of the remaining indeterminacy occurs within the entry-level name's \cluster:
the red line is computed by taking only names from the \cluster of the entry-level name into account:
by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily -- but not by much, since names for the wrong object tend not to compete for `most frequent' anyway.
(An analogous plot for the subset of all adequate names essentially coincided with the red line, reflecting that most adequate names were intended for the same object as the entry-level name.)

@@

### 2019-12-09 papers/ACL2020/related.tex
increase coherence of sections 1-2-3; shortening still required

As we outline in the following, our work on natural object naming brings together  research in psycholinguistics, \langvis and computer vision.

\paragraph{(Entry-Level) Object Naming}

%cognitive science/psychology:\\
%- levels of specificity\\
%- basic-level vs. entry-level\\ 
%- object naming studies
%
%Language + Vision:\\
%Ordonez et al., Zarriess \& Schlangen, ... \\
%- Our work: empirical notion of entry-level
%\cs{Necessary to say something about class vs. category? Otherwise I would just always use class to make things easier.}
In psycholinguistics, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}. 
The typicality of the object with respect to this basic-level \category is important for determining the preferred name, i.e.\ the entry-level name: highly typical objects (e.g.,\ a robin) are simply named by their basic-level \category (\name{bird}), while for atypical objects  (e.g.,\ \name{penguin}) the more specific name corresponds to the entry-level category. 
This strictly taxonomic view suggests that entry-level names generally hold for all instances of a \category (e.g.,\ penguin). 
\newcite{Ordonez:2016} take up this view and learn to transfer an object's \category detected by an object recognition system to its natural name, using external resources like corpus statistics. 
In contrast, our work exploits actual naming data for instances of real-world objects and tests object naming models on ManyNames, a corpus with robust name annotations from many different speakers.
This dataset is comparable to picture naming data, though we focus on real-world objects in images instead of prototypical line drawings as in, e.g.,~\newcite{rossion2004revisiting}.  
 \newcite{zarriess-schlangen:2017} learn a naming model from names produced in referring expressions to real-world objects, but they do not have access to name annotations from (many) different speakers and adopt very simple evaluation measures (like accuracy). 
Our present work explores and adopts more nuanced evaluation metrics and aims to model robust speaker preferences with respect to natural naming.
 %\sz{maybe we should not mention the Graf paper here ... we do not look at objects in context}

@@

\paragraph{Visual Object Recognition} is a major focus of research in Computer Vision, with object classification being a core task in this area. 
Neural object classification systems are trained to label the most salient object in an image and often use the ImageNet \cite{imagenet_cvpr09} benchmark that labels images/objects with 1000 fine-grained classes \cite{googlenet,he2016deep}). 
These neural object classifiers have proven extremely useful in a large range of transfer learning scenarios. They are commonly used as pretrained feature extractors in object detection systems that localize objects and predict their labels \cite{fasterrcnn2015}.
For instance, a commonly used object detector in \lv is \citep{anderson2018updown}'s so-called bottom-up model, which is based on a pretrained ResNet classification and finetunes Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg. 
We will use a pretrained ResNet, Faster-RCNN and Bottom-up as models in our work too, extending and testing them for entry-level object naming.

>>>>

%\paragraph{(Entry-Level) Object Naming}
%cognitive science/psychology:\\
%- levels of specificity\\
%- basic-level vs. entry-level\\ 
%- object naming studies
%
%Language + Vision:\\
%Ordonez et al., Zarriess \& Schlangen, ... \\
%- Our work: empirical notion of entry-level
%\cs{Necessary to say something about class vs. category? Otherwise I would just always use class to make things easier.}
Our work on natural object naming connects research in psycholinguistics, \langvis and computer vision. In psycholinguistics, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}. 
The typicality of the object with respect to this basic-level \category is important for determining the preferred name, i.e.\ the entry-level name: highly typical objects (e.g.,\ a robin) are simply named by their basic-level \category (\name{bird}), while atypical objects (e.g.,\ \name{penguin}) are preferably named by the more specific category.
%% This strictly taxonomic view suggests that entry-level names generally hold for all instances of a \category (e.g.,\ penguin).   \mw{Not true!!}
\newcite{Ordonez:2016} take up this view and train a model to map an object's \category detected by an object recognition system to its natural name, guided by external resources like corpus statistics.
By contrast, we rely on the \mn dataset (more details below) to directly test as well as fine-tune object recognition (and image classification) systems, and without presupposing a taxonomical relationship between the possible names for an object.

Our approach is closer in this regard to \newcite{zarriess-schlangen:2017}, who train an object naming model from names produced in referring expressions to real-world objects.
However, they do not have access to name annotations from (many) different annotators, and they rely on simple evaluation measures (like accuracy) whereas the additional annotations we collect enable more fine-grained evaluation.
The \mn dataset on which we rely is akin in spirit to older picture naming datasets (e.g.,~\newcite{rossion2004revisiting}) but focuses on naturalistic images of real-world objects instead of prototypical line drawings.

 %\sz{maybe we should not mention the Graf paper here ... we do not look at objects in context}

@@

In Computer Vision a major focus is visual object recognition, with object classification being a core task in this area. 
Neural object classification systems are trained to label the most salient object in an image and often use the ImageNet \cite{imagenet_cvpr09} benchmark that labels images/objects with 1000 fine-grained classes \cite{googlenet,he2016deep}). 
These neural object classifiers have proven extremely useful in a large range of transfer learning scenarios. 
They are commonly used as pretrained feature extractors in object detection systems that localize objects and predict their labels \cite{fasterrcnn2015}.
For instance, a commonly used object detector in \lv is \citep{anderson2018updown}'s so-called bottom-up model, which is based on a pretrained ResNet classification and finetunes Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg. 
We will use pretrained ResNet, Faster-RCNN and Bottom-up as models in this paper, extending and testing them for entry-level object naming.

\paragraph{The ManyNames dataset}
As mentioned we will rely heavily on the \mn dataset (Anonymous, under review), which builds upon object annotations in \vg.
\mn provides up to 36 name annotations in parallel for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
The large number of name annotations per object in \mn gives us a way to reliably derive entry-level names, defined as in Section~\ref{sec:intro} as the most frequent name for an object instance.\footnote{
	The vocabulary of all entry-level names in \mn contains 442 types (the vocabulary of all names is 7970), covering more than 50\% of the objects in \vg, i.e. almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
}
Moreover, the fact that these objects are diverse and visually situated in real-world scenes aligns with our view (see Section~\ref{sec:intro}) that entry-level name should be characterized at an instance-level, not at the class-level (cf.\ Section~\ref{sec:manynames}.
However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name.
Although these errors are interesting human data, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology that uses simple graphical boxes to point workers to the annotation target.
%used for \mn, where there is a financial incentive to complete the task as quickly as possible.
As such they pose challenges for our research goal, which is to see whether the object-naming ability of computational models resembles that of actual language users.
To overcome these we collected a new layer of verification annotations on top of \mn, as follows.
